A Formal Model of Checked C

### 2023-01-14 sandp23/implementation.tex
Minor

\noindent\emph{Handling Tainted Buffers in~\cregion}:
All buffers that are marked as tainted in~\cregion should be allocated in the sandbox. For instance,~\code{buff} in function~\code{handle_request} of~\lst{lst:final}.
We perform source rewriting and make the buffer into a pointer variable and allocate the corresponding number of bytes using the sandbox-specific allocator. For instance, we perform the following rewriting for~\code{buff} in~\lst{lst:final} with WASM sandbox.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// char buff[MAX_MSG_SIZE] __Tainted;
char *buff = ....
\end{minted}
\aravind{Arun, please fix the above example on how exactly we replace it with WASM allocator.}
Note that we also add the necessary deallocator calls at function exit points.

\noindent\emph{Handling Calls to Tainted Functions}:
In~\cregion, we also need to modify calls to tainted functions as they execute inside the sandbox (separate address space) and thus cannot be invoked as regular functions.
%\subsection{Overview}
%\systemname is implemented as a \systemname compiler and a \systemname source-level partitioning assistant (CheckMate). Given a well-typed \systemname program as an input, CheckMate performs the automation of moving the \systemname qualified function definitions to new "unchecked" source files, whilst inserting STD library headers needed for the successful compilation of these "unchecked" sources to an object file with a Sandbox-specific compiler. Since \systemname is irrelevant to the Sandbox-specific compiler, CheckMate internally runs an OCAML translator to cleanse away the \systemname annotations by converting these tainted definitions to generic-C. Now with the \systemname qualified functions and variables re-defined under the "unchecked" library object, the \systemname qualified functions definitions in the "checked" region are modified by the CheckMate accordingly to allow communication between the two regions. 
%\subsection{\systemname Function Qualifiers}
%\systemname function qualifiers are introduced with a purpose of semantic policing to allow the developer to perform dependency-resolved program partitioning into checked and unchecked regions from within the checked sources. Each of the newly introduced qualifiers "\_Tainted", "\_Mirror", "\_TLIB" and "\_Callback" enforce different semantic-ruling at compile time to allow "unchecked" and "checked" functions to communicate and access global data in a region-exclusive manner. Although checked functions are allowed to call and access "unchecked" data within the checked region, "unchecked" region can only access checked data through a specialized callback mechanism. Each of these function qualifiers differently control casting, caller, callee and data-access rules within its qualifier-scope. For example, \_TLIB qualifier allows tainted pointer parameters to be cast to non-tainted pointer arguments at the call-site of a qualified function with developer's discretion that the qualified function does not leak tainted addresses. This type-checker relaxation is granted to enable developer to avoid marshalling costs when passing tainted pointers to external library functions.

>>>>

\noindent\emph{Handling Tainted Buffers in~\cregion}:
All buffers that are marked as tainted in~\cregion should be allocated in the sandbox. For instance,~\code{buff} in function~\code{handle_request} of~\lst{lst:final}.
We perform source rewriting and make the buffer into a pointer variable and allocate the corresponding number of bytes using the sandbox-specific allocator. For instance, we perform the following rewriting for~\code{buff} in~\lst{lst:final} with WASM sandbox.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
- char buff[MAX_MSG_SIZE] __Tainted;
+ char *buff = ....
\end{minted}
\aravind{Arun, please fix the above example on how exactly we replace it with WASM allocator.}
Note that we also add the necessary deallocator calls at function exit points.

\noindent\emph{Handling Calls to Tainted Functions}:
In~\cregion, we also need to modify calls to tainted functions as they execute inside the sandbox (separate address space) and thus cannot be invoked as regular functions.
We rewrite all calls to tainted functions with corresponding sandbox invocations.
For instance, we modify the call to~\code{process_req1} in~\lst{lst:final} as below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
case REQ1: 
- rc = process_req1(buff); 
+ rc = .....
\end{minted}
\aravind{Arun, please fix the above example with the exact details.}
%\subsection{Overview}
%\systemname is implemented as a \systemname compiler and a \systemname source-level partitioning assistant (CheckMate). Given a well-typed \systemname program as an input, CheckMate performs the automation of moving the \systemname qualified function definitions to new "unchecked" source files, whilst inserting STD library headers needed for the successful compilation of these "unchecked" sources to an object file with a Sandbox-specific compiler. Since \systemname is irrelevant to the Sandbox-specific compiler, CheckMate internally runs an OCAML translator to cleanse away the \systemname annotations by converting these tainted definitions to generic-C. Now with the \systemname qualified functions and variables re-defined under the "unchecked" library object, the \systemname qualified functions definitions in the "checked" region are modified by the CheckMate accordingly to allow communication between the two regions. 
%\subsection{\systemname Function Qualifiers}
%\systemname function qualifiers are introduced with a purpose of semantic policing to allow the developer to perform dependency-resolved program partitioning into checked and unchecked regions from within the checked sources. Each of the newly introduced qualifiers "\_Tainted", "\_Mirror", "\_TLIB" and "\_Callback" enforce different semantic-ruling at compile time to allow "unchecked" and "checked" functions to communicate and access global data in a region-exclusive manner. Although checked functions are allowed to call and access "unchecked" data within the checked region, "unchecked" region can only access checked data through a specialized callback mechanism. Each of these function qualifiers differently control casting, caller, callee and data-access rules within its qualifier-scope. For example, \_TLIB qualifier allows tainted pointer parameters to be cast to non-tainted pointer arguments at the call-site of a qualified function with developer's discretion that the qualified function does not leak tainted addresses. This type-checker relaxation is granted to enable developer to avoid marshalling costs when passing tainted pointers to external library functions.
